**The status of the microbial census: an update**

### 2015-12-04 doc/notebook/Archaeal_data_acquisition.Rmd
Add EMIGRE code to work flow

```{r single_cell, engine="bash"}
mothur "#set.dir(input=data/mothur, output=data/mothur);
        align.seqs(fasta=single_cell.archaea.fasta, reference=archaea.good.fasta);
        screen.seqs(fasta=current, start=2000, end=4058, maxambig=2, maxhomop=8, minlength=900);
        classify.seqs(fasta=current, reference=archaea.good.fasta, taxonomy=archaea.good.tax, cutoff=80, processors=8)"
```

@@

```{r pool_data, engine="bash"}
cat data/mothur/archaea.good.fasta data/mothur/single_cell.archaea.good.align > data/mothur/all_archaea.align
cat data/mothur/archaea.good.tax data/mothur/single_cell.archaea.good.pds.wang.taxonomy > data/mothur/all_archaea.taxonomy

>>>>

```{r single_cell, engine="bash"}
mothur "#set.dir(input=data/mothur, output=data/mothur);
        align.seqs(fasta=single_cell.archaea.fasta, reference=archaea.good.fasta);
        screen.seqs(fasta=current, start=3000, end=7800, maxambig=2, maxhomop=8, minlength=900);
        classify.seqs(fasta=current, reference=archaea.good.fasta, taxonomy=archaea.good.tax, cutoff=80, processors=8)"
```

Once we run everything through, we see that there were 44 sequences that met our `screen.seqs` criteria.

## EMIRGE sequence data

EMIRGE is a method of either assembling 16S rRNA gene sequences from metagenomic
data or from sheared amplicons. This is a method of generating full-length
sequences using short read technologies. We've identified a handful of studies
that have used EMIRGE to generate these data and that actually made their data
publicly available. Some of these are already in the SILVA database, but many
are only available in supplementary materials or on lab websites. To generate
the pooled fasta and metadata files we run the following. Note that because
we're scraping data out of some supplements these scripts assume that you have
access to the journals...

```{r get_emirge, engine="bash"}
bash code/get_emirge_fasta.sh
bash code/get_emirge_metadata.sh
```

This will bring in 81,616 sequences: 81,608 from bacteria, 7 from archaea, and 1 from a eukaryote. We'll ignore the eukaryote. The `code/get_emirge_fasta.sh` script split the sequences by domain and put the fasta sequences into `data/mothur/` for further processing. We need to process these sequences similar to what we did with the single cell data. Because we're worried about the archaea for this notebook and there are so few, we'll process them slightly differently from the bacterial sequences by aligning them to `archaea.good.fasta`.

```{r process_emirge, engine="bash"}
mothur "#set.dir(input=data/mothur, output=data/mothur);
        align.seqs(fasta=data/mothur/emirge.archaea.fasta, reference=data/mothur/archaea.good.fasta);
        screen.seqs(fasta=current, start=3000, end=7800, maxambig=2, maxhomop=8, minlength=900);
        classify.seqs(fasta=current, reference=data/mothur/archaea.good.fasta, taxonomy=data/mothur/archaea.good.tax, cutoff=80, processors=8)"
```

Once we run everything through, we see that there were 6 sequences that met our `screen.seqs` criteria.

@@

```{r pool_data, engine="bash"}
cat data/mothur/archaea.good.fasta data/mothur/single_cell.archaea.good.align data/mothur/emirge.archaea.align > data/mothur/all_archaea.align
cat data/mothur/archaea.good.tax data/mothur/single_cell.archaea.good.good.wang.taxonomy data/mothur/emirge.archaea.good.good.wang.taxonomy > data/mothur/all_archaea.taxonomy
